---
title: "Data Cleaning"
output: 
  html_document:
        toc: TRUE
        toc_float: TRUE
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Source 

You can find the excellent article of Shilpa Arora here <https://towardsdatascience.com/dirty-data-quality-assessment-cleaning-measures-39efb90ad734>. This guide is just a summary of it.


## Priority of check 
three levels:
Level 1: Generic DQ metrics that should be checked irrespective of the type of dataset type or the use case. Few example:
-Data Type/Schema
-Missing values
-Unique Primary key
-Outliers
-Negative values, etc.
-Read more detailed Level 1 DQ metrics here.

Level 2: Contextual checks which vary across different datasets and use cases. For example:
-Column Relationship- Columns should follow their expected relation like, population column value cannot be less than household column value in the census data file.
-Contextual data range- Based on context of the data, test for expected values or range of the values like, if data is from 2014 & onwards then date can’t be before 2013.

Level 3: Comparative checks where we compare the data table with an ideal or master data table.
-Master match/Entity Resolution- Check entities like geographic names, product names, email domains etc. against standard master files to weed out bad names and replace them with correct ones.



```{r cars}
summary(cars)
```

## Including Plots

You can also embed plots, for example:

```{r pressure, echo=FALSE}
plot(pressure)
```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.
