---
title: "Data Proprocessing"
output: 
    html_document:
        toc: TRUE
        toc_float: TRUE
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
```{r klippy, echo=FALSE, include=TRUE}
klippy::klippy(position = c('top', 'right'))
```


# Introduction 

You can find the excellent article of Shilpa Arora here <https://towardsdatascience.com/dirty-data-quality-assessment-cleaning-measures-39efb90ad734>. This guide is just a summary of it.


# Priority of check 
three levels:
Level 1: Generic DQ metrics that should be checked irrespective of the type of dataset type or the use case. Few example:
-Data Type/Schema
-Missing values
-Unique Primary key
-Outliers
-Negative values, etc.
-Read more detailed Level 1 DQ metrics here.

Level 2: Contextual checks which vary across different datasets and use cases. For example:
-Column Relationship- Columns should follow their expected relation like, population column value cannot be less than household column value in the census data file.
-Contextual data range- Based on context of the data, test for expected values or range of the values like, if data is from 2014 & onwards then date can’t be before 2013.

Level 3: Comparative checks where we compare the data table with an ideal or master data table.
-Master match/Entity Resolution- Check entities like geographic names, product names, email domains etc. against standard master files to weed out bad names and replace them with correct ones.

# Preprocessing

We create a dataset to illustrate the following manipulation. 

```{r ,eval=TRUE, echo=T}
dataset <- data.frame("Country" = c('France','Spain',"Germany",'Spain',"Germany",'France',"Spain",'France',"Germany","France"),
                "Age" = c(44,27,30,38,40,35,NA,48,50,37), 
                "Salary" = c(72000,48000,54000,61000,NA,58000,52000,79000,83000,67000),
                'Purchased'=c('No','Yes','No','No','Yes','Yes','No','Yes','No','Yes'))
print(dataset)
```

## Taking care of missing data

```{r ,eval=TRUE, echo=T}
dataset$Age = ifelse(is.na(dataset$Age),
                     ave(dataset$Age, FUN = function(x) mean(x, na.rm = TRUE)),
                     dataset$Age)
dataset$Salary = ifelse(is.na(dataset$Salary),
                        ave(dataset$Salary, FUN = function(x) mean(x, na.rm = TRUE)),
                        dataset$Salary)
print(dataset)
```

## Encoding categorical data

```{r ,eval=TRUE, echo=T}
dataset$Country = factor(dataset$Country,
                         levels = c('France', 'Spain', 'Germany'),
                         labels = c(1, 2, 3))
dataset$Purchased = factor(dataset$Purchased,
                           levels = c('No', 'Yes'),
                           labels = c(0, 1))
print(dataset)
```

# Spliting the dataset into the Training set and Test set
```{r ,eval=TRUE, echo=T}
library(caTools)
set.seed(123)
split = sample.split(dataset$Purchased, SplitRatio = 0.8)
training_set = subset(dataset, split == TRUE)
test_set = subset(dataset, split == FALSE)
print(training_set)
print(test_set)
```


