---
title: "Data wrangling"
output: 
    html_document:
        toc: TRUE
        toc_float: TRUE
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
```{r klippy, echo=FALSE, include=TRUE}
klippy::klippy(position = c('top', 'right'))
```

This tutorial provides an introduction to creating websites using R, R Markdown and GitHub pages. 

This tutorial was originally presented at the Memorial Sloan Kettering Cancer Center Department of Epidemiology and Biostatistics R User Group meeting on January 23, 2018.

The current version was updated and presented at the R Ladies NYC Meetup on February 15, 2018.


## Types of websites

The main types of websites you may want to create include:

1. Personal websites
2. Package websites
3. Project websites
4. Blogs


## R Markdown website basics


The minimum requirements for an R Markdown website are:

- `index.Rmd`: contains the content for the website homepage
- `_site.yml`: contains metadata for the website

A basic example of a `_site.yml` file for a website with two pages:

```{r eval = FALSE}
name: "my-website"
navbar:
  title: "My Website"
  left:
    - text: "Home"
      href: index.html
    - text: "About"
      href: about.html
```

And a basic `index.Rmd` to create the Home page:

```{r eval = FALSE}
---
title: "My Website"
---
    
Hello, Website! Welcome to the world.
```


You can find an overview of R Markdown website basics [here](http://rmarkdown.rstudio.com/rmarkdown_websites.html).





