---
title: "Clustering"
output:
  html_document:
    toc: yes
    toc_float: yes
---
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
```{r klippy, echo=FALSE, include=TRUE}
klippy::klippy(position = c('top', 'right'))
```


Clustering is a broad set of techniques for finding subgroups of observations within a data set. When we cluster observations, we want observations in the same group to be similar and observations in different groups to be dissimilar. Because there isn’t a response variable, this is an unsupervised method, which implies that it seeks to find relationships between the n observations without being trained by a response variable. Clustering allows us to identify which observations are alike, and potentially categorize them therein. K-means clustering is the simplest and the most commonly used clustering method for splitting a dataset into a set of k groups.

We use to illustrate our code with the Hartigan (1975) City Crime database from Hartigan, J. A. (1975). Clustering Algorithms, John Wiley, New York.


```{r , echo=TRUE}
library(cluster.datasets)
data(all.us.city.crime.1970)
head(all.us.city.crime.1970,10)
city_db <- all.us.city.crime.1970[-1]
```



# K-Means Clustering

##We use the elbow method to find the optimal number of clusters

```{r message=FALSE, , echo=TRUE}
library(factoextra)
fviz_nbclust(city_db, kmeans, method = "wss", k.max = 10) + theme_minimal() + ggtitle("the Elbow Method")
```

The Elbow Curve method is helpful because it shows how increasing the number of the clusters contribute separating the clusters in a meaningful way, not in a marginal way. The bend indicates that additional clusters beyond the fourth have little value.

## Fitting K-Means to the dataset

```{r , echo=TRUE}
kmeans = kmeans(x = city_db, centers = 4)
y_kmeans = kmeans$cluster
```

## Visualising the clusters
```{r , echo=TRUE}
library(cluster)
clusplot(city_db,
         y_kmeans,
         lines = 0,
         shade = TRUE,
         color = TRUE,
         labels = 2,
         plotchar = FALSE,
         span = TRUE,
         main = paste('Clusters of customers'))
```

# Hierarchical Clustering

Hierarchical clustering is an alternative approach to k-means clustering for identifying groups in the dataset. It does not require us to pre-specify the number of clusters to be generated as is required by the k-means approach. Furthermore, hierarchical clustering has an added advantage over K-means clustering in that it results in an attractive tree-based representation of the observations, called a dendrogram.

## Using the dendrogram to find the optimal number of clusters

```{r , echo=TRUE}
dendrogram = hclust(d = dist(city_db, method = 'euclidean'), method = 'ward.D')
plot(dendrogram,
     main = paste('Dendrogram'))
```

## Fitting Hierarchical Clustering to the dataset
```{r , echo=TRUE}
hc = hclust(d = dist(city_db, method = 'euclidean'), method = 'ward.D')
y_hc = cutree(hc, 2)
```

## Visualising the clusters
```{r , echo=TRUE}
library(cluster)
clusplot(city_db,
         y_hc,
         lines = 0,
         shade = TRUE,
         color = TRUE,
         labels= 2,
         plotchar = FALSE,
         span = TRUE,
         main = paste('Clusters of customers'))
```
